Approximation as Differentiation: Notes

### 2025-07-04 notes/predicate-system.tex
First pass over predicate system for the presheaf category for C.

Now define the predicate system $\mathcal{S}^{\cat{C}}$ over $\Func{\cat{C}^\op}{\Set}$ which assigns to every
presheaf $F$ the poset $\Pred(F)$ of predicates on $F$ ordered pointwise, and where $\top, \meet, \join,
\residual$ and $\forall$ in $\Pred(F)$ are all given pointwise. For every natural transformation $\alpha: F
\to G$, define $\reindex{P}{\alpha}_X = \reindex{P_X}{\alpha_X}$ and $\directImage{P}{\alpha}_X =
\directImage{P_X}{\alpha_X}$.

>>>>

Now define the predicate system $\mathcal{S}^{\cat{C}}$ over $\Func{\cat{C}^\op}{\Set}$ which assigns to every
presheaf $F$ the poset $\Pred(F)$ of predicates on $F$ ordered pointwise, where $\top, \meet, \join,
\residual$ and $\forall$ in $\Pred(F)$ are all given pointwise, and to every natural transformation $\alpha: F
\to G$, families of pullback and pushforward maps where $\reindex{P}{\alpha}_X = \reindex{P_X}{\alpha_X}$ and
$\directImage{P}{\alpha}_X = \directImage{P_X}{\alpha_X}$.
